Last glacial cycle glacier erosion potential in the Alps

### 2021-01-18 articles/erosion/alps-erosion.tex
Introduce the three empirical studies in intro.

    While it has long been understood that glaciers leave a specific erosional
    imprint on the landscape, observing and quantifying the long-term erosion
    and sedimentation processes has been a challenge, not least due to the
    inaccessibility of glacier beds and the slow and stochastic nature of
    glacial erosion processes. More recent studies have moved away from process
    understanding in attempts to determine empirical erosion laws for an entire
    glacier or set of glaciers. \citet{Herman.etal.2015} collected sediment
    samples for \todo{X} months at the snout of Franz-Josef Glacier and mapped
    their chemical composition to different geological zones, and hence
    different glacier velocity, to construct a relationship between the
    reconstructed glacier basal velocity and the measured erosion rate.
    \citet{Koppes.etal.2015} \todo{check what they did}. \citet{Cook.etal.2020}
    \todo{check what they did}.

>>>>

    While it has long been understood that glaciers leave a specific erosional
    imprint on the landscape, observing and quantifying the long-term erosion
    and sedimentation processes has been a challenge, not least due to the
    inaccessibility of glacier beds and the slow and stochastic nature of
    glacial erosion processes. More recent studies have moved away from process
    understanding in attempts to determine empirical erosion laws for an entire
    glacier or set of glaciers. \citet{Koppes.etal.2015} quantified sediment
    yields in 15~Patagonian and Antarctic Peninsula fjords, concluding at a
    predominant control of surface air temperature on rapid glacier erosion and
    calibrating a near-square-law from glacier velocity to erosion rate.
    \citet{Herman.etal.2015} collected suspended sediment samples for 5~months
    in the outlet stream of Franz-Josef Glacier, mapped their chemical
    composition to geologic zones of distinctive glacier speed, and also
    concluded to a nearly-square relationship between from basal sliding to
    erosion rate, albeit much higher erosion rates. On the other hand,
    \citet{Cook.etal.2020} assembled a global compilation of erosion rate for
    38~glaciers, showing a predominant role of glacier sliding velocity over
    climate variables, yet concluding at a sub-linear erosion law.
